---
title: ""
output: html_document
css: "CSS.css"
---
<br><br><br><br><br><br><br><br><br><br><br><br><br>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#Necessary libraries
library(readr)
library(dplyr)
library(scales)
library(tidyverse)
library(lubridate)
library(ggthemes)

# Loading the number of births, only keeping important information for the study : sex, birth weight and birth month
if(isTRUE(getOption('knitr.in.progress'))) {
  births2018 <-
  read_fwf("../Task3/Nat2018PublicUS.c20190509.r20190717.txt",
           fwf_positions(start = c(475,504,13,9),
                         end = c(475,507,14,12),
                         col_names = c("Sex","Weight","Month","Year")
           )
  )
  births2017 <-
  read_fwf("../Task3/Nat2017PublicUS.c20180516.r20180808.txt",
           fwf_positions(start = c(475,504,13,9),
                         end = c(475,507,14,12),
                         col_names = c("Sex","Weight","Month","Year")
           )
  )
} else {
  births2018 <-
  read_fwf("Task3/Nat2018PublicUS.c20190509.r20190717.txt",
           fwf_positions(start = c(475,504,13,9),
                         end = c(475,507,14,12),
                         col_names = c("Sex","Weight","Month","Year")
           )
  )
  births2017 <-
  read_fwf("Task3/Nat2017PublicUS.c20180516.r20180808.txt",
           fwf_positions(start = c(475,504,13,9),
                         end = c(475,507,14,12),
                         col_names = c("Sex","Weight","Month","Year")
           )
  )  
}

# Merging the two
full <- bind_rows(births2017, births2018)
```

<center><h1>Study on the births in the USA from 2017 to 2018</h1><br></center>

<fieldset><center><h2>What is the proportion of boys and girls? Has it changed between 2017 and 2018?</h2><br>
```{r}
# Summarizing for sex and year for comparison
compsy <- full %>% group_by(Sex, Year) %>% summarize("Number" = n())
compsy <- compsy %>% group_by(Year) %>% mutate(Total=sum(Number), Ratio=Number*100/Total)
compsy$Year <- as.character(compsy$Year)

# Plot it, for better visualization
ggplot(compsy, aes(x = Year, y = Ratio, fill = Sex)) +
  geom_bar(stat = "identity", width = .6) +
  coord_flip() +
  ggtitle("Proportion of births of boys and girls for 2017 and 2018") +
  ylab("Percentage") +
  theme(plot.title = element_text(hjust = .5), 
        axis.ticks = element_blank()) + 
  scale_fill_brewer(palette = "Purples") +
  theme_hc()

# Average birth weight (excluding not informed weight || Weight == 9999)
full$Weight <- as.numeric(full$Weight)
avbirweight <- mean(full$Weight[full$Weight!=9999])
```
</center>
<p>The number of births of boys seems to be pretty similar to the number of births of girls, <b>as `r compsy$Ratio[[1]]` % of the births in 2017 were girls</b>, and <b>`r compsy$Ratio[[3]]` % were boys.</b></p><br>
<p>In 2018, the <b>results were similar to those of 2017</b>, as `r compsy$Ratio[[4]]` % of the births were boys and `r compsy$Ratio[[2]]` % were girls.</p><br>

<center><h2>What is the average birth weight in grams?</h2><br></center>

<p>The average birth weight of the children in the USA is <b>`r round(avbirweight, digits=0)` grams</b>, which corresponds to <b>`r round(avbirweight, digits=0)/1000` kilograms.</b></p>
</fieldset><br>

<fieldset><center><h2>Density plot of the birth weight per sex in 2018</h2><br>

```{r}
#Density plot - Weight by sex in 2018
births2018$Weight <- as.numeric(births2018$Weight)
ggplot(births2018, aes(x=round(Weight, digits=1), fill=Sex)) + 
  geom_density(alpha=0.4) +
  ggtitle("Density of birth weight per sex in 2018") +
  xlab("Weight (rounded to the first digit)") +
  ylab("Density") +
  theme_hc() +
  scale_fill_brewer(palette = "Purples") +
  scale_x_log10()
```
</center>
<p>It can be seen that both sex <b>approximately share similar weight at birth</b>. There does not seem to be a big difference between boys and girls: <b>neither is heavier than the other at birth</b>.</p>
</fieldset><br>

<fieldset><center><h2>What is the proportion of boys and girls? Has it changed between 2017 and 2018?</h2><br>
```{r}
#Does the average birth weight vary by month and year?
abwmy <- full %>% group_by(Year, Month) %>% summarize("Average_Birth_Weight" = mean(Weight))
abwmy$Month <- as.numeric(abwmy$Month)
abwmy$Year <- as.character(abwmy$Year)
ggplot(abwmy, aes(x=Month, y=Average_Birth_Weight, color=Year)) +
  geom_line(size=2) +
  ggtitle("Average birth weight per month") +
  xlab("Month") +
  ylab("Average Birth Weight") +
  scale_color_brewer(palette = "Purples") +
  theme_hc()
```
</center>
<p><b>Average birth weight seems to vary very little from years to years</b> and also seems to <b>follow the same trend</b>: for example, the average birth weight is lower in January and December in both years, compared to the other months.</p>
</fieldset><br>